Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-04 article.tex
EOD
Research hydrophobicity vs TMH vs binds MHC-I vs binds MHC-II

It is unknown if MHC-II, like MHC-I, 
present TMH-derived epitopes as as often, either 
in humans \richel{$\mathcal{H}_{2,1}$},
bacteria \richel{$\mathcal{H}_{2,2}$}
or viruses \richel{$\mathcal{H}_{2,3}$}.

@@

>>>>

It is unknown if MHC-II, like MHC-I, 
presents TMH-derived epitopes as often, either 
in humans \richel{$\mathcal{H}_{2,1}$},
bacteria \richel{$\mathcal{H}_{2,2}$}
or viruses \richel{$\mathcal{H}_{2,3}$}.

@@

Transition matrix from \cite{dang2010flu}.
